The \dealii Library, Version 9.0

### 2018-05-13 9.0/paper.tex
Add release date.

\dealii version 9.0.0 was released April X, 2018.
\marginpar{Update the date}
This paper provides an
overview of the new features of this major release and serves as a citable
reference for the \dealii software library version 9.0. \dealii is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
GNU Lesser General Public License (LGPL) from the \dealii homepage at
\url{http://www.dealii.org/}.

@@

\dealii and its developers are financially supported through a
variety of funding sources:
\marginpar{all: update your funding sources}

>>>>

\dealii version 9.0.0 was released May 11, 2018.
This paper provides an
overview of the new features of this major release and serves as a citable
reference for the \dealii software library version 9.0. \dealii is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
GNU Lesser General Public License (LGPL) from the \dealii homepage at
\url{http://www.dealii.org/}.

@@

\dealii and its developers are financially supported through a
variety of funding sources:
